---
title: "R Notebook"
author  : Eagle Xuhui Ying
date    : 10/24/2022 
output: 
  html_document:
    toc: true
    toc_depth: 3
    theme: paper
    highlight: tango
    df_print: paged
---


# Libraries  

```{r, eval=TRUE, warning=FALSE, message=FALSE}
options(warn = -1)
library(tidyverse)
library(tidymodels)
library(janitor)
library(skimr)
library(kknn)
library(ggplot2)
```

## 1. Import Data
```{r, eval=TRUE, warning=FALSE, message=FALSE}
churn <- read_csv("Churn_training.csv") %>% clean_names() 

head(churn)

churn_kaggle <- read_csv("Churn_holdout.csv") %>% clean_names() 

head(churn_kaggle)
```

## 2. Explore Target

```{r, eval=TRUE, warning=FALSE, message=FALSE}
churn_summary <- churn %>%
  count(churn) %>%
  mutate(pct = n/sum(n))

churn_summary %>%
  ggplot(aes(x=factor(churn),y=pct)) +
  geom_col()  + 
  geom_text(aes(x=factor(churn),y=pct+0.034, label = round(pct*100,2)), vjust = 2.25, colour = "white") +
  labs(title="Customer Churn ", x="Churn", y="PCT")
```

## 3. Explore your data 
```{r, eval=TRUE, warning=FALSE, message=FALSE}
churn %>% skimr::skim_without_charts()
```
## Explore numerics 

numeric variables: monthly_minutes, customer_service_calls, streaming_minutes, total_billed, prev_balance, late_payments, number_phones

```{r, eval=TRUE, warning=FALSE, message=FALSE}

# -- comparative boxplots

boxplot <- function(m){
    ggplot(churn, aes(x=!!as.name(m), y=as.factor(churn), fill=as.factor(churn))) + 
    geom_boxplot() +
    labs(title = as.character(m), y = 'churn') +
    theme(legend.title = element_blank()) 
}

numerics <- c('monthly_minutes', 'customer_service_calls', 'streaming_minutes', 'total_billed', 'prev_balance', 'late_payments', 'number_phones')

for (c in numerics){
    print(boxplot(c))
}

```

## Explore character variables  

categorical variables: phone_model, partner, phone_service, multiple_lines, streaming_plan, mobile_hotspot, wifi_calling_text, online_backup, paperless_billing, payment_method, gender, network_speed, senior_citizen

```{r, eval=TRUE, warning=FALSE, message=FALSE}

churn$senior_citizen <- as.factor(churn$senior_citizen)
churn_kaggle$senior_citizen <- as.factor(churn_kaggle$senior_citizen)

char_explore <- function(col){
    churn %>%
    ggplot(aes(!!as.name(col))) + 
    geom_bar(aes(fill = as.factor(churn))) +
    coord_flip() +
    theme(legend.title = element_blank())
}

dummy <- c('phone_model', 'partner', 'phone_service', 'multiple_lines', 'streaming_plan', 'mobile_hotspot', 'wifi_calling_text', 'online_backup', 'paperless_billing', 'payment_method', 'gender', 'network_speed', 'senior_citizen')

# -- for each character column, create a chart
for (column in dummy){
    chrt <- char_explore(column)
    print(chrt)
}
```

## 4. Transform 
Convert categories to factors 
```{r, eval=TRUE, warning=FALSE, message=FALSE}
churn_prep <- churn %>%
   mutate(churn = as.factor(churn)) %>%
   mutate_if(is.character, factor) 

churn_prep %>% head()

churn_kaggle <- churn_kaggle %>% 
   mutate_if(is.character, factor) 
```

## 5. Partition your data into 70/30 train/test split 

```{r, eval=TRUE, warning=FALSE, message=FALSE}
set.seed(123)
x <- initial_split(churn_prep, prop = 0.7, strata = churn)
train <- training(x)
test  <- testing(x)

sprintf("Train PCT : %1.2f%%", nrow(train)/nrow(churn_prep) * 100)
sprintf("Test  PCT : %1.2f%%", nrow(test)/nrow(churn_prep) * 100)
```

## 6. Define Recipe 

```{r, eval=TRUE, warning=FALSE, message=FALSE}
knn_recipe <- recipe(churn ~ monthly_minutes + customer_service_calls + streaming_minutes + total_billed + prev_balance + late_payments + phone_model + partner + phone_service + multiple_lines + streaming_plan + mobile_hotspot + wifi_calling_text + online_backup + number_phones + paperless_billing + payment_method + gender + network_speed + senior_citizen, data=train) %>%
    step_impute_median(all_numeric_predictors()) %>%
    step_unknown(all_nominal_predictors()) %>%
    step_scale(all_numeric_predictors()) %>%
    step_dummy(all_nominal_predictors())

knn_recipe

gc()

# eyeball recipe results 
bake(knn_recipe %>% prep(), train, composition = "tibble") %>% head()
```

## 7. Define your Model(s)

```{r, eval=TRUE, warning=FALSE, message=FALSE}
knn_model <- nearest_neighbor(neighbors = 7) %>%
    set_mode("classification") %>%
    set_engine("kknn")

knn_model_2 <- nearest_neighbor(neighbors = 10) %>%
    set_mode("classification") %>%
    set_engine("kknn")

```

## 8. Workflow 

```{r, eval=TRUE, warning=FALSE, message=FALSE}
knn_workflow <- workflow() %>%
    add_recipe(knn_recipe) %>%
    add_model(knn_model) %>%
    fit(train)

knn_workflow_2 <- workflow() %>%
    add_recipe(knn_recipe) %>%
    add_model(knn_model_2) %>%
    fit(train)
```

## 9. Score the model

```{r, eval=TRUE, warning=FALSE, message=FALSE}
options(yardstick.event_first = TRUE)
# -- score training  
scored_train <- predict(knn_workflow, train, type="prob") %>%
    bind_cols(predict(knn_workflow, train, type="class")) %>%
    bind_cols(.,train) 
# -- score testing 
scored_test <- predict(knn_workflow, test, type="prob") %>%
    bind_cols(predict(knn_workflow, test, type="class")) %>%
    bind_cols(.,test)

scored_train_2 <- predict(knn_workflow_2, train, type="prob") %>%
    bind_cols(predict(knn_workflow_2, train, type="class")) %>%
    bind_cols(.,train) 
# -- score testing 
scored_test_2 <- predict(knn_workflow_2, test, type="prob") %>%
    bind_cols(predict(knn_workflow_2, test, type="class")) %>%
    bind_cols(.,test)
```

## 10. Evaluate (KNN = 7)

```{r, eval=TRUE, warning=FALSE, message=FALSE}
options(yardstick.event_first = FALSE)
# -- Metrics: Train and Test 
scored_train %>% 
    metrics(churn, .pred_1, estimate = .pred_class) %>%
    mutate(part="training") %>%
    bind_rows(scored_test %>% 
                 metrics(churn, .pred_1, estimate = .pred_class) %>%
                 mutate(part="testing") ) %>%
    filter(.metric %in% c('accuracy','roc_auc')) %>%
    pivot_wider(names_from = .metric, values_from=.estimate)
  
# -- ROC Charts 
scored_train %>%
  mutate(model = "train") %>%
  bind_rows(scored_test %>%
              mutate(model="test")) %>%
  group_by(model) %>%
  roc_curve(churn, .pred_1) %>%
  autoplot()
  
scored_train %>%
  precision(churn, .pred_class) %>%
  mutate(part="training") %>%
  bind_rows(
  scored_test %>%
  precision(churn,.pred_class) %>%
    mutate(part="testing"))

scored_train %>%
  recall(churn, .pred_class) %>%
  mutate(part="training") %>%
  bind_rows(
  scored_test %>%
  recall(churn,.pred_class) %>%
    mutate(part="testing") 
  )

scored_train %>%
  conf_mat(
  truth = churn,
  estimate = .pred_class,
  dnn = c("Prediction", "Truth")
) %>%
  autoplot(type = "heatmap") + 
  labs(title="Training Confusion Matrix")

scored_test %>%
  conf_mat(
  truth = churn,
  estimate = .pred_class,
  dnn = c("Prediction", "Truth")
) %>%
  autoplot(type = "heatmap") + 
  labs(title="Testing Confusion Matrix")
```

## Evaluate (KNN = 10)

```{r, eval=TRUE, warning=FALSE, message=FALSE}
options(yardstick.event_first = FALSE)
# -- Metrics: Train and Test 
scored_train_2 %>% 
    metrics(churn, .pred_1, estimate = .pred_class) %>%
    mutate(part="training") %>%
    bind_rows(scored_test_2 %>% 
                 metrics(churn, .pred_1, estimate = .pred_class) %>%
                 mutate(part="testing") ) %>%
    filter(.metric %in% c('accuracy','roc_auc')) %>%
    pivot_wider(names_from = .metric, values_from=.estimate)
  
# -- ROC Charts 
scored_train_2 %>%
  mutate(model = "train") %>%
  bind_rows(scored_test_2 %>%
              mutate(model="test")) %>%
  group_by(model) %>%
  roc_curve(churn, .pred_1) %>%
  autoplot()
  
scored_train_2 %>%
  precision(churn, .pred_class) %>%
  mutate(part="training") %>%
  bind_rows(
  scored_test_2 %>%
  precision(churn,.pred_class) %>%
    mutate(part="testing"))

scored_train_2 %>%
  recall(churn, .pred_class) %>%
  mutate(part="training") %>%
  bind_rows(
  scored_test_2 %>%
  recall(churn,.pred_class) %>%
    mutate(part="testing") 
  )

scored_train_2 %>%
  conf_mat(
  truth = churn,
  estimate = .pred_class,
  dnn = c("Prediction", "Truth")
) %>%
  autoplot(type = "heatmap") + 
  labs(title="Training Confusion Matrix")

scored_test_2 %>%
  conf_mat(
  truth = churn,
  estimate = .pred_class,
  dnn = c("Prediction", "Truth")
) %>%
  autoplot(type = "heatmap") + 
  labs(title="Testing Confusion Matrix")
```

## Kaggle 

```{r, eval=TRUE, warning=FALSE, message=FALSE}
# -- score testing 
kaggle_prediction <- predict(knn_workflow, churn_kaggle, type="class") %>%
    bind_cols(., churn_kaggle) %>%
    select(customer_id, churn=.pred_class)
  
kaggle_prediction %>% 
  write_csv("challenge_1_kaggle.csv")
```
